---
title: "sta 141a HW2"
output: html_document
---

Daocheng Zhang
918331476

```{r}
library(tidyverse)
library(nycflights13)
```


1.
```{r}
dim(iris)
head(iris)
```

This dataset is a build-in dataset. It shows the speal length, with, petal length, and width for fifty flowers from three species of iris. This dataset is interesting because it is a well-known and widely used dataset in the field of statistics and machine learning. It gives detailed data of different flowers. 



2.
(i)
```{r}


dim(flights)
```
There are 336776 observations and 19 variables

(ii)
**tailnum** means the plane tail number.
**flight** means the flight number.
**carrier** means two letter carrier abbreviation.
**dep_delay** and **arr_delay** represent departure and arrival delays. If the number is negative, it represents early departures or arrivals.

(iii)
**visib** means visibility in miles.
**time_hour** means the date and hour
**temp** means temperature in F


3.
```{r}

library(tidyverse)

alaska_flights <- data.frame(flights %>% filter( carrier=='AS'))
early_january_weather<- data.frame(weather%>% filter(origin=='EWR', month=="1"))

```


4.
```{r}
plot(x=alaska_flights$dep_delay,y=alaska_flights$arr_delay, 
     xlab= "dep_delay", 
     ylab= "arr_delay",
     pch=16,
     col= alpha("black", alpha = 1) )
     
```
We could notice that dep_delay and arr_delay are positive corelated. The reason is that when the departure is delayed, arrival is also delayed, if the flight time remains same. 




5.
```{r}
plot(x=alaska_flights$dep_delay,y=alaska_flights$arr_delay, 
     xlab= "dep_delay", 
     ylab= "arr_delay",
     pch=16,
     col= alpha("black", alpha = 0.2) )
     
```
By comparing two plots, we could notice that the color of each dot in the second plot is lighter. Therefore, it is easier to find out where all points concentrate. 


6.
```{r}

plot(x= early_january_weather$time_hour, y=early_january_weather$temp, 
     xlab = "time_hour",
     ylab= "temp",
     type="l")
```
From Jan 21 to 28, the tempterature drops significantly. 

7.
```{r}
set.seed(1)
n=100
x<- c(runif(n,min=-2,max=2))
z<- c(rnorm(n,mean=0,sd=sqrt(0.5)))
e<- c(rnorm(n,mean=0,sd=sqrt(1)))
beta.true=c(1,2,1)
y<- x*beta.true[1] + beta.true[2]*z + beta.true[3]*x*z + e
lm(y ~x)
```
8.
```{r}
simulate<- function(x,beta.true,z){
  x<- c(runif(n,min=-2,max=2))
  z<- c(rnorm(n,mean=0,sd=sqrt(0.5)))
  e<- c(rnorm(n,mean=0,sd=sqrt(1)))
  beta.true=c(1,2,1)
  y<- x*beta.true[1] + beta.true[2]*z + beta.true[3]*x*z +  e
  lm(y ~ x)
  return(lm(y~x)$coef[2])
}
N.sim=5000;
set.seed(1)
n=100;
beta.true=c(1,2,1)
sim= replicate(N.sim,simulate(x,beta.true,z))
sim.mean= mean(sim)
result<- data.frame(sim)
ggplot(result, aes(x = sim)) +
  geom_histogram(binwidth = 0.05, color = "black", fill = "white")+
  geom_vline(xintercept = sim.mean, color = "black",linewidth = 1, linetype = "solid") +
  geom_vline(xintercept = 1, color = "red", linewidth = 1,linetype = "dashed")+
  labs(x = "Coefficient", y = "Frequency")

```
It is easily to notice that our simulation mean is very close to the true value.


9.
```{r}
print(sim.mean)
simulate<- function(x,beta.true,z){
  x<- c(runif(n,min=-2,max=2))
  z<- c(rnorm(n,mean=0,sd=sqrt(0.5)))
  e<- c(rnorm(n,mean=0,sd=sqrt(1)))
  beta.true=c(1,2,1)
  y<- x*beta.true[1] + beta.true[2]*z + beta.true[3]*x*z +  e
  lm(y ~ x)
  return(lm(y~x)$coef[2])
}
N.sim=4000;
set.seed(1)
n=100;
beta.true=c(1,2,1)
sim= replicate(N.sim,simulate(x,beta.true,z))
sim.mean= mean(sim)
print(sim.mean)
```
Both of them have very similar mean.


10.
```{r}
simulate<- function(x,beta.true,z){
  x<- c(runif(n,min=-2,max=2))
  e_hat<- c(rnorm(n,mean=0,sd=sqrt(0.5)))
  z<- x+1+e_hat
  e<- c(rnorm(n,mean=0,sd=sqrt(1)))
  y<- x*beta.true[1] + beta.true[2]*z  + e
  lm(y ~ x)
  return(lm(y~x)$coef[2])
}
N.sim=5000
n=100
beta.true=c(1,2)
sim= replicate(N.sim,simulate(x,beta.true,z))
sim.mean= mean(sim)
print(sim.mean)
```
Therefore, the estimator for the coefficient of x is not unbiased.


#### **Acknowledgement**
Using Chatgpt, I learned how to change the transparency in problem 4 and 5.I also learned how to draw the histogram in problem 8.
https://openai.com/blog/chatgpt


For problem 6, I draw a linegraph using the content from Math Insight
https://mathinsight.org/image/r_line_graph_1 
